Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-04 paper/main.tex
Updates

\section{Background and Related Work}
\label{sec:background}
\subsection{Notations}
We denote random variables with uppercase letters $ X $, and a set of random
variables as $ \bm{X} = \{X_1, \cdots, X_k\} $ with $ \rvert \bm{X} \rvert = k
$. A sample from the random variable $ X $ is denoted as $ x $ and from a set
of random variables $ \bm{X} $ is denoted as $ \bm{x} $. In this paper, we
consider random variables in the mixed data setting where each of the random
variables can be either of continuous, categorical, or ordinal unless
specified.

We write the expectation of a variable $ X $ as $ \mathbb{E}[X] $, conditional
expectations as $ \mathbb{E}[X | \bm{Z}] $.

>>>>

\section{Background and Related Work}
\label{sec:background}
\subsection{Notations}
\todo[inline]{Improve this section once all the notations are in place}
We denote random variables with uppercase letters $ X $, and a set of random
variables as $ \bm{X} = \{X_1, \cdots, X_k\} $ with $ \rvert \bm{X} \rvert = k
$. A sample from the random variable $ X $ is denoted as $ x $ and from a set
of random variables $ \bm{X} $ is denoted as $ \bm{x} $. In this paper, we
consider random variables in the mixed data setting where each of the random
variables can be either of continuous, categorical, or ordinal unless
specified. We write the expectation of a variable $ X $ as $ \mathbb{E}[X] $, conditional
expectations as $ \mathbb{E}[X | \bm{Z}] $.
